---
title: "RPart1_Homework"
author: "NYC Data Science Academy"
output:
  pdf_document: default
  html_document: default
---
## Question #1	

Compound interest can be computed using the formula
$$A = P (1+\frac{r}{100}) ^n$$
where P is the original money lent, A is what it amounts to in n years at R percent per year interest. Write an R command to calculate a vector of numbers indicating the amount of money owed (A) after n years, where n ranges from 1 to 15 in yearly increments. The original amount lent is 5000 dollars (P) and the interest rate remains constant throughout the period at 11.5% (r). 

```{r Question 1}
n = 1:15
P = 5000
r = .115
A = P*((1+ r)^n)


```

## Question #2

Assume that we have collected the heights and weights of four people. The heights (in cm) are 180, 165, 160, 193; the respective weights (in kg) are 87, 58, 65, 100. Create two vectors, `height` and `weight`, using the data. Body mass index (BMI) is defined as
$$BMI = \frac{mass_{kg}}{height_{m}^2}$$
Write an R command to make a vector calculating the BMI values for the four people. Be careful of the units! As a challenge, use the height vector to make a boolean vector named `tall` of the heights above 6 feet.

```{r Question 2}
height = c(180, 165, 160, 193)
weight = c(87, 58, 65, 100)

BMI =  (weight)/(height/100)

tall = height > 182.88

```


## Question #3:

1. From your RStudio, import the built-in cars dataset by running `data(cars)`.

2. Print the first 5 lines from cars.

3. Randomly generate a vector as long as the the number of rows in cars containing elements NY, CA or CT. Call the vector `state`. Run the code `set.seed(0)` on the line above your vector. This makes your results reproducible (anybody who runs the code `set.seed(0)` on their randomized vector will end up with the same random vector you generated). 

4. Add state to the data frame cars as a new column. Again name the column `state`.

5. Create a new column `ratio` whose value is the ratio `dist`/`speed`. Then compute the average and standard deviation of that column.

```{r Question 3}
#1.
data(cars)

#2.
head(cars, n =5) 

#3 
set.seed(0)
state = sample(x = c('NY', 'CA', 'CT'), size = length(cars$speed), replace = TRUE)


#4.
cars$state = sample(x = c('NY', 'CA', 'CT'), size = length(cars$speed), replace = TRUE)

#5.

cars$ratio = (cars$dist/cars$speed)

mean(cars$ratio)
sd(cars$ratio)
```


## Question #4: 

Read the `TimesSquareSignage.csv` and import it into R as `ts_data`. Then check the following features of the dataset:

1. The number of observations and the number of variables.

2. The type (`class`) of each variable.

3. How many missing values are there in the dataset?

4. Which rows (people) have missing values? Which columns (variables) include missing values?

```{r Question 4}
ts_data = read.csv('https://s3.amazonaws.com/graderdata/TimesSquareSignage.csv', stringsAsFactors=FALSE)

# 1.
nrow(ts_data)

#2.
sapply(ts_data,class)

#3.
sum(is.na(ts_data))

#4.
View(ts_data)

which(is.na(ts_data$Screen.Name..LED...Vinyl.Signs.))

colSums(is.na(ts_data))
```

## Question #5:

From the Time Square dataset, we'd like to extract specific information about advertising in Midtown Manhattan. Obtain the following data frames and save them in a subfolder named `data` in your current directory as CSV files:

1. Observations from Upper Broadway. Save as `UpperBway.csv`.

2. Observations with greater-than-average square footage. Save as `SF.csv`.

3. The name, address, and location of the ten signs with the largest total square footage. Save as `TopTen.csv`. 

```{r Question 5}

#1.
ts_data = data.frame(ts_data)
UpperBway <- ts_data[ts_data$Location	 == "Upper Bway",]
write.csv(UpperBway,'UpperBway.csv',row.names=FALSE)

#2.
mean_sf = mean(ts_data$SF)
SF <- ts_data[ts_data$SF>mean_sf,]
write.csv(SF, 'SF.csv',row.names=FALSE)

#.3
TopTen = ts_data[order(-ts_data$TOTAL.SF),][1:10,c(1,2,4)]
write.csv(TopTen, 'TopTen.csv',row.names=FALSE)
```




