---
title: "RPart2_Homework"
author: "NYC Data Science Academy"
output: html_document
---
## Question #1	

Each new term in the Fibonacci sequence is generated by adding the previous two terms. Starting with 1 and 2, the first 10 Fibonacci numbers are:

1, 2, 3, 5, 8, 13, 21, 34, 55, 89,...

Consider all the Fibonacci numbers whose values do not exceed four million. Find the sum of even-valued terms among them.

```{r Question 1}

fib <- c(1, 2)  #Define first two numbers
while (max(fib) < 4e+06) {
    # Generate Fibonacci numbers until limit is reached
    len <- length(fib)
    fib <- c(fib, fib[len - 1] + fib[len])
}
answer <- sum(fib[fib%%2 == 0])


```

## Question #2

Write your own code to implement the multiplication between a matrix and a vector. In case you forget it, here's the definition of matrix multiplication. For an m?n matrix A and an n-dimensional vector x, y = Ax is an m-dimensional vector, where 
$$\begin{align}y[i] = \sum_{j=1}^nA[i,j]x[j] \text{ for } i = 1,2,3,...m\end{align}$$

```{r Question 2}
mat = matrix(1:15, nrow = 3, ncol = 5)
vec = matrix(1:5, nrow = 5, ncol = 1)
res = c()
func <- function(mat,vec) {
  if (ncol(mat) != nrow(vec)) {
    return("Bad Math")
  }
  for(row in 1:nrow(mat)) {
    for(col in 1:ncol(mat)) {
       res <- append(res,mat[row, col]*vec[row])
  }

  }
  add <- matrix(res , nrow = nrow(mat),ncol = ncol(mat), byrow = TRUE)
  total <- rowSums(add)
  return(total)
}

total <- func(mat,vec)
```

## Question #3:

Write a function that calculates the median absolute deviation (MAD) of a numeric vector. The median absolute deviation is a robust alternative to standard deviation as a measure of dispersion. For vector X, it is defined as  
$$MAD = median(|X_i-median(X)|)$$
```{r Question 3}
n = c(3,76,32,6,7,62,12)
mad <- function(n) {
  md = median(n)
  x = abs(n-md)
  y = median(x)
  return(y)
}

mad(n)
     
```


## Question #4: 

Suppose we have a  character vector as follows: `Names <- "John Andrew Thomas"`
Write some R code to obtain the following output:

 $$\begin{align}\text{"John@gmail.com; Andrew@gmail.com; Thomas@gmail.com"}\end{align}$$

```{r Question 4}
Names <- "John Andrew Thomas"
N = unlist(strsplit(Names, split=" "))
N = gsub(" ", "", N)
G = paste(N, "@gmail.com", sep = '')
gsub(";","",toString(G))
sapply(x,tolower)
```

## Question #5:

Write R code to generate a vector with the following elements, **without using loops**.

"aa" "ba" "ca" "da" "ea" "ab" "bb" "cb" "db" "eb" "ac" "bc" "cc" "dc" "ec" "ad" "bd" "cd" "dd" "ed" "ae" "be" "ce" "de" "ee"

```{r Question 5}
x = c('a','b','c','d','e')
y = c('a','b','c','d','e')
y = rep(y, c(4,4,4,4,4))
z = paste(x,y,sep='')
z

```

## Question #6:

Write an R function named `compare` which takes two words as arguments/inputs and returns "Equal Length" if the number of characters are equal in two words and "Not Equal Length" otherwise. It should work as following: 
```
>>compare("EPS568","Summer") 
"Equal Length"					
>>compare("EPS568","SummerA") 
"Not Equal Length"
```
```{r Question 6}
compare <- function(a,b)
{
  if (nchar(a) != nchar(b)) {
    return("Not Equal Length")
  }
  return("Equal Length")
}

```

## Challenge Question:

The game of craps is played as follows:

* Roll two six-sided dice; let x be the sum of the dice on the first roll.
* If x is 7 or 11, you automatically win.
* If x is 2, 3 or 12, you lose.
* If x is any other value (4, 5, 6, 8, 9, 10), x is then called the "point". Continue to re-roll the dice until you either roll the "point" again or a 7. 
    + If you obtain the established point x again, you win.
    + If a 7 is rolled before the point, you lose.


1. Write an R function to play this game once all the way through. You can use the expression 
`x <- sum(sample(1:6, 2, replace=T))` 
to simulate the sum of two rolled dice. The outcome of this expression should be a character element of either "Win" or "Loss".

2. Now, use the R expression you develop in (1), and repeat this game 1000 times hypothetically using a *for loop*. You should save the result of 1000 games in a vector with each element is either "Win" or "Loss". 

```{r Challenge Question}
x <- sum(sample(1:6, 2, replace=T))
win = 'win'
 switch(win,
win = (x=8),
lose = (x=2),
point = (x=8)
)


 
age_type = 'middle'
age = sample(0:100, 20, replace=TRUE)
switch(age_type,
young = age[age <= 30],
middle = age[age <= 70 & age > 30],
old = age[age > 70]
)

```





